---
title: "SRT411 Assignment 0"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## ToDo 3.1

Compute the difference between 2014 and the
year you started at this university and divide
this by the difference between 2014 and the year
you were born. Multiply this with 100 to get
the percentage of your life you have spent at
this university. Use brackets if you need them.

```{r }
abs((2014 - 2014)/(2014 - 1979)) * 100
```

## ToDo 3.2

Repeat the previous ToDo, but with several
steps in between. You can give the variables
any name you want, but the name has to start
with a letter.

```{r }
my_birthdate <- 1979
my_collegedate <- 2014
abs((my_collegedate - 2014)/(my_birthdate - 2014)) * 100
```

## ToDo 3.4

Compute the sum of 4, 5, 8 and 11 by first combining
them into a vector and then using the
function sum.

```{r}
sum(c(4, 5, 8, 11))
```

## ToDo 3.5

Plot 100 normal random numbers.

```{r}
plot(rnorm(100))
```

## ToDo 4

Find help for the sqrt function

```{r}
help(sqrt)
```

## ToDo 5

Make a file called firstscript.R containing Rcode
that generates 100 random numbers and
plots them, and run this script several times.

```{r}
source('~/Desktop/SRT411/assignment0/firstscript.r')
```

## ToDo 6.2

Put the numbers 31 to 60 in a vector named
P and in a matrix with 6 rows and 5 columns
named Q. Tip: use the function seq. Look at
the different ways scalars, vectors and matrices
are denoted in the workspace window.

```{r}
p <- seq(31,60)
Q <- matrix(p, nrow = 6, ncol = 5, byrow = FALSE, dimnames = NULL)
p
Q
```

## ToDo 6.3

Make a script file which constructs three random
normal vectors of length 100. Call these
vectors x1, x2 and x3. Make a data frame called
t with three columns (called a, b and c) containing
respectively x1, x1+x2 and x1+x2+x3.
Call the following functions for this data frame:
plot(t) and sd(t). Can you understand the
results? Rerun this script a few times.

content of file ~/Desktop/SRT411/assignment0/script-6.3.r
x1 <- rnorm(100)
x2 <- rnorm(100)
x3 <- rnorm(100)
t <- data.frame(a = x1, b = x1 + x2, c = x1 + x2 + x3)
plot(t)

```{r}
source('~/Desktop/SRT411/assignment0/script-6.3.r')
```

## ToDo 7

Add these lines to the script file of the previous
section. Try to find out, either by experimenting
or by using the help, what the meaning is of
rgb, the last argument of rgb, lwd, pch, cex.

content of file ~/Desktop/SRT411/assignment0/script-7.r
x1 <- rnorm(100)
x2 <- rnorm(100)
x3 <- rnorm(100)
t <- data.frame(a = x1, b = x1 + x2, c = x1 + x2 + x3)
plot(t$a, type="l", ylim=range(t),lwd=3, col=rgb(1,0,0,0.3))
lines(t$b, type="s", lwd=2,col=rgb(0.3,0.4,0.3,0.9))
points(t$c, pch=20, cex=4,col=rgb(0,0,1,0.3))

```{r}
source('~/Desktop/SRT411/assignment0/script-7.r')
```

## ToDo 8

Make a file called tst1.txt in Notepad from
the example in Figure 4 and store it in your
working directory. Write a script to read it, to
multiply the column called g by 5 and to store
it as tst2.txt.

The content of the file tst2.txt
"a" "g" "x"
1 10 3
2 20 6
4 40 12
8 80 24
16 160 48
32 320 96

```{r}
d = read.table(file="~/Desktop/SRT411/assignment0/tst1.txt", header=TRUE)
d1 <- data.frame(a = d$a, g = d$g *5, x = d$x)
write.table(d1, file="~/Desktop/SRT411/assignment0/tst2.txt",row.names=FALSE)
```

## ToDo 9

Compute the mean of the square root of a vector
of 100 random numbers. What happens?

```{r}
mean(sqrt(rnorm(100)))
```

## ToDo 10.2

Make a graph with on the x-axis: today, Sinterklaas
2014 and your next birthday and on
the y-axis the number of presents you expect on
each of these days. Tip: make two vectors first.

```{r}

```

## ToDo 11.2

Make a vector from 1 to 100. Make a for-loop
which runs through the whole vector. Multiply
the elements which are smaller than 5 and larger
than 90 with 10 and the other elements with 0.1.

```{r}
a = seq(1, 100)
s = c()
for(i in a)
{
  if(a[i] < 5 | a[i] > 90)
  {
    s[i] = a[i] * 10
  }  
  else
  {
    s[i] = a[i] * 0.1
  }  
}
s
```

## ToDo 11.3

Write a function for the previous ToDo, so
that you can feed it any vector you like
(as argument). Use a for-loop in the function
to do the computation with each element.
Use the standard R function length
in the specification of the counter. a
)

```{r}
fun11.3 = function(arg1)
{
  s = c()
  for(i in (1:length(arg1)))
  {
    if(arg1[i] < 5 | arg1[i] > 90) 
    {
      s[i] = arg1[i]  * 10
    }
    else
    {
      s[i] = arg1[i] * 0.1 
    }
  }
  return(s)
}

fun11.3(seq(3,95))
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
